Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-11-01 paper/lncsFormat.tex
before modifying

%TODO 这个table需要增加BTM生成的和aviation最相近的一个topic的情况。
\hlgreen{TODO: add a new table, containing a topic generated by BTM, which is most similar to the extracted topic from KB.}
\begin{table}[]
\centering
\scalebox{0.76}{
\begin{tabular}{|c|c|l|c|}
\hline
\#group* & \#word*  & words & NPMI\\ \hline
0 & 6-10 & airlines aviation flying pilot squadron &  0.113\\ \hline
1 & 11-15 &flights pilots raf airways fighter & 0.155\\ \hline
2 & 16-20 &boeing runway force crashed flew   & 0.092\\ \hline
3 & 21-25 &airfield landing passengers plane aerial & 0.179\\ \hline
4 & 26-30 &bomber radar wing bombers crash & 0.137\\ \hline
5 & 31-35 &airbus airports operations jet helicopter & 0.189\\ \hline
6 & 36-40 &squadrons base flown havilland crew & 0.088\\ \hline
7 & 41-45 &combat luftwaffe aerodrome carrier fokker & 0.159\\ \hline
8 & 46-50 &planes fly engine takeoff fleet & 0.186\\ \hline
9 & 51-55 &fuselage helicopters aviator naval aero & 0.157\\ \hline
10 & 56-60 &glider command training balloon faa & 0.166\\ \hline
\(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\)\\ \hline
18 & 96-100 &scheduled carriers military curtiss biplane &0.131\\ \hline
19 & 101-105 &accident engines iaf albatross rcaf &0.068\\ \hline
\end{tabular}
}
\caption{Top words' topic coherence of \textit{Aviation}'s history state. * means the group also contains the five top words \textit{aircraft}, \textit{air}, \textit{airport}, \textit{flight}, and \textit{airline}, but we don't show them in table to save space. NPMI is computed on ten words (a combination of words in each row with the five top words).}
\label{tbl:NPMIDetails}
\end{table}

@@

\begin{table*}[ht]
\centering
\scalebox{0.76}{
\begin{tabular}{|cc|cc|cc|cc|cc|cc|}
\hline
\multicolumn{2}{|c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Middle East}} & \multicolumn{2}{c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Mobile Phones}}\\
\begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} \\ 
\hline
aircraft & air & health & weight & al & \textbf{\textit{\#syria}} & army & killed & android & iphone\\ 
air & plane & patients & loss & israel & \textbf{\textit{\#bahrain}} & military & news & mobile & apple \\ 
airport & flight & medical & diet & iran & people & air & \textbf{\textit{\#libya}} & nokia & android \\ 
flight & time & disease & health & arab & israel & command & libya & ios & app \\
airline & airlines & treatment & cancer & israeli & police & force & rebels & phone & ipad \\
airlines & news & hospital & lose & egypt & \textbf{\textit{\#libya}} & regiment & people & samsung & samsung \\
aviation & boat & patient & fat & egyptian & \#egypt & forces & police & game & mobile\\
flying & airport & clinical & tips & ibn & news & squadron & war & app & blackberry \\
pilot & force & symptoms & treatment & jerusalem & \textbf{\textit{\#israel}} & infantry & libyan & iphone & tablet \\
squadron & fly & cancer & body & syria & world & battle & attack & htc & apps\\
\hline
\end{tabular}
}
\caption{Category-Level Topics extracted from knowledge base and the corresponding topics on microblog stream learned from CTrans-LDA, taking the categories \textit{Aviation},  \textit{Health}, \textit{Middle East}, \textit{Military}, and \textit{Mobile Phones} as examples. The words in \textbf{\textit{bold italic}} font are newly learned on the microblog stream by the transfer learning, which semantic meanings are verified consistent with the categories; while the black words play the role as the bridge in transfer learning, and appear in the both category-level topics in two domains.}
\label{tbl:historyStates}
\end{table*}
%TODO: add the top words in the category-level topic 
\hlgreen{TODO: add the top words of the category-level topic in each window of microblog stream AFTER Table 2.}

@@

%TODO LSH-FSD\cite{Petrovic:2010uj}没有评测FSD的情况，我们也可以提一句，我们不评测FSD，我们只评测检测出的事件是否是真实的事件。
\hlgreen{TODO: check the number of detected events.}
\begin{table}[h]
\scriptsize
\centering
\scalebox{0.95}{
    \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}F@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
    LSH & 0.824 & 0.095 & 0.803 & - & 0.302 \\ \hline
    TimeUserLDA & 0.353 & 0.536 & 0.071 & - & 0.054 \\ \hline
    Twevent & 0.824 & 0.697 & 0.641 & - & 0.113 \\ \hline
    EDCoW & 0.412 & 0.756 & 0.119 & - & 0.290 \\ \hline
    BurstyBTM & 0.647 & 0.809 & 0.170 & - & 0.045 \\ \hline
    \textsc{TransDetector} & 1.000 & 0.894 & 0.950 & - & 0.042 \\ \hline
    \end{tabular}
}
\caption{Overall Performance on Event Detection}
\end{table}

\begin{table}
\centering
\caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-28}
\label{my-label}
\scalebox{0.77}{
\begin{threeparttable}  
\begin{tabular}{|c|l|l|c|l|l|l|l|l|l|}
\hline
\multirow{2}{*}{Date} & \multirow{2}{*}{Event key words} & \multirow{2}{*}{Representative event tweet} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular}} & \multicolumn{6}{c|}{Methods\tnote{a}} \\ \cline{5-10} 
 &  &  &  & L & TU & TW & E & B & TD \\ \hline
7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman... http://dlvr.it/cLbk8\end{tabular} & 557 & \checkmark &  &  &  &  &  \\ \hline
7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 & \checkmark &  &  &  &  &  \\ \hline
7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 47 & \checkmark &  &  &  &  &  \\ \hline
7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 52 & \checkmark &  &  &  &  &  \\ \hline
7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 & \checkmark &  &  &  &  &  \\ \hline
\end{tabular}

>>>>

%TODO 这个table需要增加BTM生成的和aviation最相近的一个topic的情况。
\hlgreen{TODO: add a new table, containing a topic generated by BTM, which is most similar to the extracted topic from KB.}
\begin{table}[]
\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
\setlength{\belowcaptionskip}{0.cm}
\centering
\caption{Top words' topic coherence of \textit{Aviation}'s history state. * means the group also contains the five top words \textit{aircraft}, \textit{air}, \textit{airport}, \textit{flight}, and \textit{airline}, but we don't show them in table to save space. NPMI is computed on ten words (a combination of words in each row with the five top words).}
\scalebox{0.76}{
\begin{tabular}{|c|l|l|l !{\vrule width 1pt} c|l|l|l|}
\hline
\multicolumn{4}{|c!{\vrule width 1pt}}{TransDetector} & \multicolumn{4}{c|}{LightLDA}    \\ \hline
\#group*  & \#words*  & words  & NPMI & \#group* & \#words* & words & NPMI \\ \hline
0 & 6-10 & airlines aviation flying pilot squadron &  0.113 & 0 & 6-10 & & \\ \hline
1 & 11-15 &flights pilots raf airways fighter & 0.155 & 1 & 11-15 & & \\ \hline
2 & 16-20 &boeing runway force crashed flew   & 0.092 & 2 & 16-20 & & \\ \hline
3 & 21-25 &airfield landing passengers plane aerial & 0.179 & 3 & 21-25 & & \\ \hline
4 & 26-30 &bomber radar wing bombers crash & 0.137 & 4 & 26-30 & & \\ \hline
5 & 31-35 &airbus airports operations jet helicopter & 0.189 & 5 & 31-35 & & \\ \hline
6 & 36-40 &squadrons base flown havilland crew & 0.088 & 6 & 36-40 & & \\ \hline
7 & 41-45 &combat luftwaffe aerodrome carrier fokker & 0.159 & 7 & 41-45 & & \\ \hline
8 & 46-50 &planes fly engine takeoff fleet & 0.186 & 8 & 46-50 & & \\ \hline
9 & 51-55 &fuselage helicopters aviator naval aero & 0.157 & 9 & 51-55 & & \\ \hline
10 & 56-60 &glider command training balloon faa & 0.166 & 10 & 56-60 & & \\ \hline
\(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\) & \(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\)\\ \hline
18 & 96-100 &scheduled carriers military curtiss biplane &0.131 & 11 & 96-100 & & \\ \hline
19 & 101-105 &accident engines iaf albatross rcaf &0.068 & 12 & 101-105 & & \\ \hline
\end{tabular}
}
\label{tbl:NPMIDetails}
\end{table}

@@

\begin{table*}[ht]
\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
\setlength{\belowcaptionskip}{0.cm}
\centering
\caption{Category-Level Topics extracted from knowledge base and the corresponding topics on microblog stream learned from CTrans-LDA, taking the categories \textit{Aviation},  \textit{Health}, \textit{Middle East}, \textit{Military}, and \textit{Mobile Phones} as examples. The words in \textbf{\textit{bold italic}} font are newly learned on the microblog stream by the transfer learning, which semantic meanings are verified consistent with the categories; while the words in normal font play the role as the bridge in transfer learning, and appear in the both category-level topics in two domains.}
\scalebox{0.8}{
\begin{tabular}{|cc|cc|cc|cc|cc|cc|}
\hline
\multicolumn{2}{|c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Middle East}} & \multicolumn{2}{c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Mobile Phones}}\\
\begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} \\ 
\hline
aircraft & air & health & weight & al & \textbf{\textit{\#syria}} & army & killed & android & iphone\\ 
air & plane & patients & loss & israel & \textbf{\textit{\#bahrain}} & military & news & mobile & apple \\ 
airport & flight & medical & diet & iran & people & air & \textbf{\textit{\#libya}} & nokia & android \\ 
flight & time & disease & health & arab & israel & command & libya & ios & app \\
airline & airlines & treatment & cancer & israeli & police & force & rebels & phone & ipad \\
airlines & news & hospital & lose & egypt & \textbf{\textit{\#libya}} & regiment & people & samsung & samsung \\
aviation & boat & patient & fat & egyptian & \#egypt & forces & police & game & mobile\\
flying & airport & clinical & tips & ibn & news & squadron & war & app & blackberry \\
pilot & force & symptoms & treatment & jerusalem & \textbf{\textit{\#israel}} & infantry & libyan & iphone & tablet \\
squadron & fly & cancer & body & syria & world & battle & attack & htc & apps\\
\hline
\end{tabular}
}
\label{tbl:historyStates}
\end{table*}
%TODO: add the top words in the category-level topic 
\hlgreen{TODO: add the top words of the category-level topic in each window of microblog stream AFTER Table 2.}

@@

%TODO LSH-FSD\cite{Petrovic:2010uj}没有评测FSD的情况，我们也可以提一句，我们不评测FSD，我们只评测检测出的事件是否是真实的事件。
\hlgreen{TODO: check the number of detected events.}
\begin{table}[h]
\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
\setlength{\belowcaptionskip}{0.cm}
\centering
\caption{Overall Performance on Event Detection}
\scriptsize
\scalebox{0.95}{
    \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}F@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
    LSH & 0.824 & 0.095 & 0.803 & - & 0.302 \\ \hline
    TimeUserLDA & 0.353 & 0.536 & 0.071 & - & 0.054 \\ \hline
    Twevent & 0.824 & 0.697 & 0.641 & - & 0.113 \\ \hline
    EDCoW & 0.412 & 0.756 & 0.119 & - & 0.290 \\ \hline
    BurstyBTM & 0.647 & 0.809 & 0.170 & - & 0.045 \\ \hline
    \textsc{TransDetector} & 1.000 & 0.894 & 0.950 & - & 0.042 \\ \hline
    \end{tabular}
}
\end{table}

\begin{table}
\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
\setlength{\belowcaptionskip}{0.cm}
\centering
\caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-28}
\label{my-label}
\scalebox{0.77}{
\begin{threeparttable}  
\begin{tabular}{|c|l|l|c|l|l|l|l|l|l|}
\hline
\multirow{2}{*}{Date} & \multirow{2}{*}{Event key words} & \multirow{2}{*}{Representative event tweet} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular}} & \multicolumn{6}{c|}{Methods\tnote{a}} \\ \cline{5-10} 
 &  &  &  & L & TU & TW & E & B & TD \\ \hline
7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman... http://dlvr.it/cLbk8\end{tabular} & 557 & \checkmark &  &  &  &  &  \\ \hline
7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 & \checkmark &  &  &  &  &  \\ \hline
7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 47 & \checkmark &  &  &  &  &  \\ \hline
7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 52 & \checkmark &  &  &  &  &  \\ \hline
7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 & \checkmark &  &  &  &  &  \\ \hline
\end{tabular}
